Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-05-10 paper.tex
Minor spellings in related work

Magana et al.~\cite{magana2019remote} compared in 2019 the most popular remote desktop protocols and software implementations. The authors analyzed five protocols: PCoIP used in the Amazon WorkSpaces, RDP, TeamViewer, VNC, and Citrix Independent Computing Architecture (ICA). In the paper, the network transfer rate and its relation to the quality experienced by the DaaS user are evaluated by assuming three scenarios: using an office software suite, web browsing, and video streaming. One emphasis of the paper is comparing the transfer rate of the different protocols for three scenarios. In the Office Software Suite scenario, the transfer rate is measured and compared when performing several tasks like opening and editing a document (typing), loading an image, and saving a document. The web browsing scenario covers requesting three different web pages, and for the video streaming scenario, the same YouTube video file was viewed at different resolutions. The authors conclude that RDP requires fewer downstream and upstream network resources for all three scenarios. It is important to understand that the protocols RDP and VNC are implemented in open-source projects and proprietary solutions for many different operating systems. Depending on the various quality levels of the many existing implementations, it is difficult to generalize about the performance of the protocols, as individual implementations may have better or worse performance characteristics than expected.

>>>>

Magana et al.~\cite{magana2019remote} compared in 2019
the most popular remote desktop protocols and software implementations.
The authors analyzed five protocols:
PCoIP used in the Amazon WorkSpaces, RDP, TeamViewer, VNC,
and Citrix Independent Computing Architecture (ICA).
In the paper, the network transfer rate and its relation to the quality
experienced by the DaaS user are evaluated
by assuming three scenarios:
using an office software suite, web browsing, and video streaming.
One emphasis of the paper is comparing the transfer rate
of the different protocols for three scenarios.
In the Office Software Suite scenario,
the transfer rate is measured and compared
when performing several tasks like opening
and editing a document (typing), loading an image, and saving a document.
The web browsing scenario covers requesting three different web pages,
and for the video streaming scenario,
the same YouTube video file was viewed at different resolutions.
The authors conclude that RDP requires fewer downstream
and upstream network resources for all three scenarios.
Generally can be said, that protocols RDP and VNC
are among the most popular frame-buffer protocols
which are utilized in countless open-source and proprietary projects
for different operating systems.
Depending on the various quality levels of the many existing implementations,
it is difficult to generalize about the performance of the protocols,
as individual implementations may have better
or worse performance characteristics than expected.
